Supplemental Materials, Methods and Results

### 2021-05-06 supp.Rmd
Updated style tables and supplement. Corrected a few errors

>>>>

```{r tableS5, tab.cap = "Linear mixed effects model results using sandwich estimators and Saitterwaite degrees of freedom correction."}
robust_sc_table <- rbind(robust_ConspicDisplayAC,
                          robust_ConspicDisplayCC,
                          robust_ConspicCourtshipAC,
                          robust_ConspicCourtshipCC) %>% 
                    mutate(p_Satt = sapply(p_Satt, function(x) p_value(x)),
                           SocialContext = c("Male-Male Display", rep("", 17), 
                                             "Courtship Display", rep("", 17)),
                           JND = c("Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8), 
                                   "Achromatic Contrast", rep("", 8), 
                                   "Chromatic Contrast", rep("", 8)))

robust_sc_table$parameter <- rownames(robust_sc_table)

robust_sc_table <- robust_sc_table %>% select(SocialContext, JND, parameter, beta, SE, tstat, df, p_Satt)

tableS5 <- flextable(robust_sc_table) %>%  table_style4()
tableS5
```
